\documentclass{article}

\begin{document}

\begin{abstract}
This paper benchmarks hardware and software implementation of GCD. Hardware assisted implementation was written using VHDL and is faster than software based one. Acceleration of crucial mathematical algorithms matters in comptuer science, including information security.
\end{abstract}

\section{Introduction}

Working of RSA algorithm is heavily based upon computations on primary numbers. Two large prime numbers are generated and speed of generation and validation of these is crucial. Speeding up processes would let us break the RSA.

In this paper we will present software and hardware assisted implementations of GCD.

\section{Method}

\subsection{Software based implementation of GCD}

\subsection{Hardware-assisted implementation of the GCD algorithm}

Hardware implementation is done in VHDL. GCD implementation is created in VHDL and so was the testbench.

\subsection{Implementation details of GCD}

\subsubsection{Processes}

There are two processes in the program:

\begin{itemize}
\item State updater - Reacts to clock and reset signal. On clock event, all variables with suffix \texttt{next} are copied to variables of type \texttt{current}.
\item Logic - State machines
\end{itemize}

The implementation is based on state machine, which are specific case of finite automata. This automata consists of four states:

\begin{itemize}
\item \texttt{idle}
\item \texttt{start}
\item \texttt{shift}
\item \texttt{sub}
\end{itemize}

The process starts in \texttt{idle} state and continues to \texttt{start} state. The \texttt{busy} flag is lit and the process jumps between \texttt{shift} and \texttt{sub} until contents of \texttt{a\_reg} and \texttt{b\_reg} are equivalent. The \texttt{busy} flag is no longer lit and result is written out.

Optimizations can be done. This is not the fastest implementation of GCD known. It is possible that the states \texttt{idle} and \texttt{start} are redundant, but this project aims to present a sample implementation of GCD.

\section{Results}

\end{document}
